An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-12-29 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Adding sigma tables created by macros.

\usepackage{wrapfig}    % Allows wrapping of text around figures
\usepackage{soul}       % Provides strikethrough text
\usepackage{float}      % Allows precise positioning of tables and figures within the text
\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow}   % To create multirow tables
\usepackage{hyperref}   % To create hyperlinks in the paper
\usepackage{microtype}  % produces hanging punctuation and beautiful type
\usepackage{booktabs}   % produces beautiful tables

@@

@@

%++++++++++++++++++++++++++++++
\subsection{Are the World Bank country categories
helpful for conceptualizing the role of energy in economic growth?} 
\label{sec:wb_categories_helpful}
%++++++++++++++++++++++++++++++

@@

\begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
  \begin{center}
    \begin{tabular}{r l c l c l c} 
      \toprule
         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
      \midrule
      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
                                        &  & 
                                              & &  \\
                                  & ($\underline{kl}$)$e$ & C 
                                        & ($\underline{ek}$)$l$ & $\sim\sim\sim$ 
                                              & ($\underline{le}$)$k$ & $\sim\sim\sim$ \\
      \midrule
      \multirow{3}{*}{$\sigma$} & &
                                      & ($\underline{k}l$)$\underline{e}$ & $\sim\sim\sim$
                                            & ($k\underline{l}$)$\underline{e}$ & $\sim\sim\sim$ \\
                                & ($\underline{l}e$)$\underline{k}$ & C
                                      & ($l\underline{e}$)$\underline{k}$ & C
                                            &  & \\
                                & ($e\underline{k}$)$\underline{l}$ & C
                                      & &
                                            & ($\underline{e}k$)$\underline{l}$ & C \\
      \midrule
                                & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table} \caption{Elasticities of substitution (UK).} \label{tab:sigma_UK} 
  \begin{center}
    \begin{tabular}{r l c l c l c} 
      \toprule
         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
      \midrule
      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
                                        &  & 
                                              & &  \\
                                  & ($\underline{kl}$)$e$ & $\sim\sim\sim$ 
                                        & ($\underline{ek}$)$l$ & C
                                              & ($\underline{le}$)$k$ & C \\
      \midrule
      \multirow{3}{*}{$\sigma$} & &
                                      & ($\underline{k}l$)$\underline{e}$ & C
                                            & ($k\underline{l}$)$\underline{e}$ & C \\
                                & ($\underline{l}e$)$\underline{k}$ & C
                                      & ($l\underline{e}$)$\underline{k}$ & C
                                            &  & \\
                                & ($e\underline{k}$)$\underline{l}$ & $\sim\sim\sim$
                                      & &
                                            & ($\underline{e}k$)$\underline{l}$ & $\sim\sim\sim$ \\
      \midrule
                                & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

>>>>

\usepackage{wrapfig}    % Allows wrapping of text around figures
\usepackage{soul}       % Provides strikethrough text
\usepackage{float}      % Allows precise positioning of tables and figures within the text
\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow}   % To create multirow tables
\usepackage{hyperref}   % To create hyperlinks in the paper
\usepackage{microtype}  % produces hanging punctuation and beautiful type
\usepackage{booktabs}   % produces beautiful tables
\usepackage{tablefootnote}  % allows footnotes in tables

@@

% The following commands assist making tables for elasticity of substitution (sigma and sigma_1).
% The \firstrow macro creates the sigma_1 row.  The following arguments apply:
% #1 sigma_1 for (kl) nest
% #2 sigma_1 for (kl)e nest
% #3 sigma_1 for (ek)l nest
% #4 sigma_1 for (le)k nest
\newcommand{\firstrow}[4]{\multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & #1 
                                  &  & 
                                        & &  \\
                            & ($\underline{kl}$)$e$ & #2
                                  & ($\underline{ek}$)$l$ & #3
                                        & ($\underline{le}$)$k$ & #4 \\
}

% The \secondrow macro creates the sigma row.  The following arguments apply:
% #1 sigma for (kl)e nest
% #2 sigma for (kl)e nest
% #3 sigma for (le)k nest
% #4 sigma for (le)k nest
% #5 sigma for (ek)l nest
% #6 sigma for (ek)l nest
\newcommand{\secondrow}[6]{      \multirow{3}{*}{$\sigma$} & &
                                      & ($\underline{k}l$)$\underline{e}$ & #1
                                            & ($k\underline{l}$)$\underline{e}$ & #2 \\
                                & ($\underline{l}e$)$\underline{k}$ & #3
                                      & ($l\underline{e}$)$\underline{k}$ & #4
                                            &  & \\
                                & ($e\underline{k}$)$\underline{l}$ & #5
                                      & &
                                            & ($\underline{e}k$)$\underline{l}$ & #6 \\
}

% The \thirdrow macro creates the summary row at the bottom.  The following arguments apply:
% #1 summary for elasticity of substitution between k and l
% #2 summary for elasticity of substitution between k and e
% #3 summary for elasticity of substitution between l and e
\newcommand{\thirdrow}[3]{    & \multicolumn{2}{c}{#1} & \multicolumn{2}{c}{#2} & \multicolumn{2}{c}{#3} \\ }

% The \eostable macro creates the overall table.  
% The label for the table is tab:sigma_#1, i.e., tab:sigma_<2-letter country code>.  
% The following arguments apply:
% #1 2-letter country abbreviation
% #2 sigma_1 row.  Use \firstrow macro here.
% #3 sigma row.  Use \secondrow macro here.
% #4 summary row.  Use \thirdrow macro here.
\newcommand{\eostable}[4] {\begin{table} \caption{Elasticities of substitution (#1).} \label{tab:sigma_#1} 
  \begin{center}
    \begin{tabular}{r l c l c l c} 
      \toprule
         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
      \midrule
      #2
      \midrule
      #3
      \midrule
      #4
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}
}

@@

%++++++++++++++++++++++++++++++
\subsection{Are the World Bank country categories
helpful for understanding the role of energy in economic growth?} 
\label{sec:wb_categories_helpful}
%++++++++++++++++++++++++++++++

@@

% \begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
%   \begin{center}
%     \begin{tabular}{r l c l c l c} 
%       \toprule
%          & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
%       \midrule
%       \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
%                                         &  & 
%                                               & &  \\
%                                   & ($\underline{kl}$)$e$ & C 
%                                         & ($\underline{ek}$)$l$ & $\sim\sim\sim$ 
%                                               & ($\underline{le}$)$k$ & $\sim\sim\sim$ \\
%       \midrule
%       \multirow{3}{*}{$\sigma$} & &
%                                       & ($\underline{k}l$)$\underline{e}$ & $\sim\sim\sim$
%                                             & ($k\underline{l}$)$\underline{e}$ & $\sim\sim\sim$ \\
%                                 & ($\underline{l}e$)$\underline{k}$ & C
%                                       & ($l\underline{e}$)$\underline{k}$ & C
%                                             &  & \\
%                                 & ($e\underline{k}$)$\underline{l}$ & C
%                                       & &
%                                             & ($\underline{e}k$)$\underline{l}$ & C \\
%       \midrule
%                                 & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
%       \bottomrule
%     \end{tabular}
%   \end{center}
% \end{table}

% label is tab:sigma_US
\eostable{US}
          {\firstrow{C}{C}{$\sim\sim\sim$}{$\sim\sim\sim$}}
          {\secondrow{$\sim\sim\sim$}{$\sim\sim\sim$}{C}{C}{C}{C}}
          {\thirdrow{C}{C}{C}}

% label is tab:sigma_UK
\eostable{UK}
          {\firstrow{C}{$\sim\sim\sim$}{C}{C}}
          {\secondrow{C}{C}{C}{C}{$\sim\sim\sim$}{$\sim\sim\sim$}}
          {\thirdrow{C}{C}{C}}

% label is tab:sigma_JP
\eostable{JP}
          {\firstrow{c}{C}{$\sim\sim\sim$}{C}}
          {\secondrow{C}{C}{C}{C}{C}{C}}
          {\thirdrow{C}{C}{C}}

% label is tab:sigma_CN
\eostable{CN}
          {\firstrow{$\sim\sim\sim$}{C}{C}{S}}
%           {\secondrow{S {\scriptsize (driven by $le$?)}}{S}{C}{C}{c}{c {\scriptsize (driven by $kl$?)}}}
          {\secondrow{S\tablefootnote{Driven by $le$?}}{S}{C}{C}{c}{c\tablefootnote{Driven by $kl$?}}}
          {\thirdrow{C}{C}{S}}

% label is tab:sigma_ZA
\eostable{ZA}
          {\firstrow{c$\sim$}{$\sim\sim\sim$}{C}{$\sim\sim\sim$}}
          {\secondrow{C}{C}{C}{C}{$\sim\sim\sim$}{C\tablefootnote{Points on right are all same.}}}
          {\thirdrow{c}{C}{C}}

% label is tab:sigma_SA
\eostable{SA}
          {\firstrow{c$\sim$}{$\sim\sim\sim$}{C}{$\sim\sim\sim$}}
          {\secondrow{C}{C}{C}{C}{$\sim\sim\sim$}{C\tablefootnote{Points on right are all same.}}}
          {\thirdrow{c}{C}{C}}
